### 2017-05-04 localizations.tex
working

>>>>

In general, we expect {\tt Repair} to be used in the context of
compiler (or other complex system) fuzzing, where there are numerous
failing tests, likely from multiple faults.  In such cases, the $f$ to
be localized is presumably selected by FPF.  However, in case our
localization approach is used in a setting where single faults are
expected, we propose an alternative method: let $f$ be an arbitrary test
test with as few repairing mutants as possible.
